Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
replace "ising" by "izing"

Program synthesizers are an ideal fit for synthesis of %parametric
digital controllers, since the semantics of programs capture effects such as FWL
precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
for the synthesis of switching controllers for stabilising continuous-time
plants with polynomial dynamics.  The work extends to affine systems, 
finding a major challenge in the hardness of solving linear arithmetic with the state-of-the-art SMT solvers.  
Since this approach uses switching models instead of linear dynamics for the digital controller, 
it entirely circumvents the FWL problem, but potentially incurs state-space explosion issues.  
This approach is not suitable for the kind of control we seek to synthesise.

%\textcolor{red}{Cristina: can you please revise this sentence:
Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
use a CEGIS-based approach for synthesising continuous-time switching
controllers that guarantee \emph{reach-while-stay} properties of closed-loop systems, 
i.e., properties that specify a set of goal states and safe states (constrained reachability).%}. 
The solution is based on synthesising control Lyapunov 
functions for switched systems, that yield switching controllers with
a guaranteed minimum dwell time in each mode.

The work in \cite{DBLP:journals/corr/AbateBCCDKK16} investigates the synthesis of 
stabilising controllers for continuous plants described as transfer functions, 
by exploiting bit-accurate verification of software-implemented 
digital controllers~\cite{Bessa16}.  While this work also make use of a CEGIS-based technique, 
the approach is restricted to synthesising digital controllers for stable 
closed-loop systems described via transfer function models.  
In contrast, in the current paper we consider a state-space representation of the physical system, 
which is known to be more general \cite{Astrom08} and allows to synthesise controllers that
make the closed-loop system \emph{safe}.  Moreover, 
this work  integrates an abstraction/refinement step inside the main CEGIS loop.

The tool Pessoa~\cite{mazo2010pessoa} is a MatLab toolbox that synthesises correct-by-design
embedded control software. It is based on the description of a physical system
as an equivalent finite-state machine and on the computation of reachability properties over the finite-state 
machine. 
Based on this safety specification over state values, 
Pessoa can synthesise embedded controller software for a range of properties.  
%based on a safety specification over state values, as well as specification on characteristic functions of the controller. 
However, Pessoa does not have native inclusion of the ADC/DAC quantisation error needed for
synthesising fixed-point digital controllers.

@@

As mentioned earlier, 
in this work we are not bound to the synthesis of digital stabilising controllers -- 
a well known task in the literature on digital control system -- 
but target safety requirements with an overall approach that is sound and automated. 
More specifically, 
we require that the closed-loop system \eqref{eq:closedloopss} meets given safety specifications. 
A safety specification raises a requirement on the states of the model, 
such that the feedback controller (namely the choice of the gains in $K$) 
must ensure that the states never exist such requirement. 
Note that a stable, closed-loop system is not necessarily a safe system: 
indeed, the state values may leave the safe whilst they converge to the equilibrium, 
which is typical in the case of oscillatory dynamics.

@@

%% This technique relies on parametrising the target language, which
%% induces a lattice of progressively more expressive languages 
%% \textcolor{red}{Cristina: Citation?}.  We
%% start by attempting to synthesise a program at the lowest point on
%% this lattice and increase the parameters of the language until we
%% reach a point at which the synthesis succeeds. As well as giving us an
%% automatic search procedure, this parametrisation greatly increases the
%% efficiency of our system since languages low down the lattice are very
%% easy to decide safety for (i.e. the validation oracle finds an answer
%% fast). If a program can be synthesised in a low-complexity language,
%% the whole procedure finishes much faster than if synthesis had been
%% attempted in a high-complexity language.

>>>>

Program synthesizers are an ideal fit for synthesis of %parametric
digital controllers, since the semantics of programs capture effects such as FWL
precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
for the synthesis of switching controllers for stabilizing continuous-time
plants with polynomial dynamics.  The work extends to affine systems, 
finding a major challenge in the hardness of solving linear arithmetic with the state-of-the-art SMT solvers.  
Since this approach uses switching models instead of linear dynamics for the digital controller, 
it entirely circumvents the FWL problem, but potentially incurs state-space explosion issues.  
This approach is not suitable for the kind of control we seek to synthesise.

%\textcolor{red}{Cristina: can you please revise this sentence:
Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
use a CEGIS-based approach for synthesizing continuous-time switching
controllers that guarantee \emph{reach-while-stay} properties of closed-loop systems, 
i.e., properties that specify a set of goal states and safe states (constrained reachability).%}. 
The solution is based on synthesizing control Lyapunov 
functions for switched systems, that yield switching controllers with
a guaranteed minimum dwell time in each mode.

The work in \cite{DBLP:journals/corr/AbateBCCDKK16} investigates the synthesis of 
stabilizing controllers for continuous plants described as transfer functions, 
by exploiting bit-accurate verification of software-implemented 
digital controllers~\cite{Bessa16}.  While this work also make use of a CEGIS-based technique, 
the approach is restricted to synthesizing digital controllers for stable 
closed-loop systems described via transfer function models.  
In contrast, in the current paper we consider a state-space representation of the physical system, 
which is known to be more general \cite{Astrom08} and allows to synthesise controllers that
make the closed-loop system \emph{safe}.  Moreover, 
this work  integrates an abstraction/refinement step inside the main CEGIS loop.

The tool Pessoa~\cite{mazo2010pessoa} is a MatLab toolbox that synthesises correct-by-design
embedded control software. It is based on the description of a physical system
as an equivalent finite-state machine and on the computation of reachability properties over the finite-state 
machine. 
Based on this safety specification over state values, 
Pessoa can synthesise embedded controller software for a range of properties.  
%based on a safety specification over state values, as well as specification on characteristic functions of the controller. 
However, Pessoa does not have native inclusion of the ADC/DAC quantisation error needed for
synthesizing fixed-point digital controllers.

@@

As mentioned earlier, 
in this work we are not bound to the synthesis of digital stabilizing controllers -- 
a well known task in the literature on digital control system -- 
but target safety requirements with an overall approach that is sound and automated. 
More specifically, 
we require that the closed-loop system \eqref{eq:closedloopss} meets given safety specifications. 
A safety specification raises a requirement on the states of the model, 
such that the feedback controller (namely the choice of the gains in $K$) 
must ensure that the states never exist such requirement. 
Note that a stable, closed-loop system is not necessarily a safe system: 
indeed, the state values may leave the safe whilst they converge to the equilibrium, 
which is typical in the case of oscillatory dynamics.

@@

%% This technique relies on parametrizing the target language, which
%% induces a lattice of progressively more expressive languages 
%% \textcolor{red}{Cristina: Citation?}.  We
%% start by attempting to synthesise a program at the lowest point on
%% this lattice and increase the parameters of the language until we
%% reach a point at which the synthesis succeeds. As well as giving us an
%% automatic search procedure, this parametrisation greatly increases the
%% efficiency of our system since languages low down the lattice are very
%% easy to decide safety for (i.e. the validation oracle finds an answer
%% fast). If a program can be synthesised in a low-complexity language,
%% the whole procedure finishes much faster than if synthesis had been
%% attempted in a high-complexity language.
